\LARGE \bf Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty

### 2014-12-30 paper.tex
added stuff

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

@@

\overrideIEEEmargins                                      % Needed to meet printer requirements.

@@

\usepackage{tikz,hyperref,graphicx,units,subfig}
\usepackage{benktools}
\usepackage{caption}
\renewcommand{\captionfont}{\footnotesize}
\usepackage{sidecap,wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\abs}[1]{\lvert#1\rvert} 
\newcommand{\norm}[1]{\lVert#1\rVert}
%\newcommand{\suchthat}{\mid}
\newcommand{\suchthat}{\ \big|\ }
\newcommand{\bd}{\mathbf{d}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bt}{\mathbf{t}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bbf}{\mathbf{f}}
\newcommand{\bzero}{\mathbf{0}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mF}{\mathcal{F}}
\newcommand{\bZ}{\mathbf{Z}}

@@

\begin{abstract}
Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.  This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
\end{abstract}

@@

@@

In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps . $P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed. Reducing the time to find the best expected grasp from a set of a large number of grasps is the primary focus of the paper.

For shape we use a GPIS representation, which is explained in detail in Sec. \ref{sec:Appendix}. Essentially, a GPIS is a Gaussian distribution on a signed distance function that describes the workspace. The GPIS can be sampled from via $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS. For our application we set $x$ to discretized points along each line of action $\gamma_i$ and for each sample see where the sample is equal to zero.  We will furthermore represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.

@@

 \vspace{-2ex}
 \begin{align*}
 &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
 &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\Delta)
 \end{align*}

@@

\subsection{Multi-Armed Bandit Experiments}
\todo{Running experiments over break, going to fill this in as results come in}
We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$. For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. In Fig. \ref{fig:simple_regret}, we plotted the simple regret averaged over 100 of the shapes in our data set and compare the different methods (UCB, Thompson, Gittins and the naive random allocation). We initialize both the Monte-Carlo and bandit technique by sampling each grasp 1 time. We draw samples from our calculated distributions $p(g)$.  Interestingly, Gittins and Thompson converge much faster than random and UCB. In Fig. \ref{fig:pulls_per_grasp}, you can see that Gittins and Thompson allocate grasp samples to only the grasps of high quality, thus it is quickly able to ignore the low quality grasps. UCB takes a more conservative approach to sample allocation, which leads to poor performance in the best arm identification problem \cite{bubeck2009pure}.

@@

\subsection{Sensitivity Analysis }
We now will show how well the top two algorithms (Thompson and Gittens) perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose. The experiments are performed with the same setup as before but now we sweep the variance parameters across a range for each parameter. The results are shown below

\todo{Finish sensitivity analysis}

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_rot.eps}
\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins). Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape. As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation. UCB does poorly on simple regret which is expected \cite{best_arm}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_trans.eps}
\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins). Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape. As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation. UCB does poorly on simple regret which is expected \cite{best_arm}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_fric.eps}
\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins). Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape. As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation. UCB does poorly on simple regret which is expected \cite{best_arm}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

@@

Our budgeted multi-armed bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids. Future work will be building an efficient construction of GPIS to scale to 3D and test the bandit method there. While we have seen the bandit method always converge to the correct value in our experiments, our method only has a statistical guarantee of doing so. A non-optimal grasp plan could be found, albeit with a low probability.

Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{mahler2015opt}.

An additional problem is that we only have an expected center of mass and not a distribution on the center of mass. This might prove to be to expensive to compute, however recent work by Panahi et al. showed a way to bound the center of mass for convex parts. Extension of his work to implicit surfaces could be of possible interest \cite{panahi2014bounding}.  When using the shape sampling approach on the GPIS instead of sampling along the grasp plan trajectory, the center of mass is easy to compute on a sampled shape, so this is a limitation of our sampling method.

\section{Conclusion}
Assessing grasp quality under shape uncertainty is computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under shape uncertainty. 
A key insight from our work is that uniformly allocating samples to grasps is inefficient, and
 we found that the Successive Elimination multi-armed bandit approach prioritizes evaluation of high-quality grasps while quickly pruning-out obviously poor grasps.
A pre-requisite for applying a bandit approach is to formulate an efficient representation of how shape uncertainty affects grasp parameters and thus grasp quality.
We modeled uncertainty with Gaussian process implicit surfaces (GPIS) and derived the distribution of grasp parameters when a nominal grasp is applied to the GPIS.
As a result, we were able to more efficiently sample from a distribution of grasps executions rather than the shape; leading to a complexity improvement of $n^3$ in the resolution of the discretization $n$.
We evaluated this theoretical model on a dataset of common objects and confirmed that: (1) the bandits approach always converged to the best grasp in the candidate set, (2) it converges on average an order of magnitude faster than a uniform sampling approach in our experiments, and (3) sampling from the grasp contacts is 12x faster than sampling from shapes for a 64x64 grid.

@@

Future work will also consider applying BMAB approach to grasp planners like GraspIt! \cite{miller2004graspit} to see if our method can handle uncertainty while working under the time constraints needed for most real time applications. We currently have only tested one bandit algorithm, successive elimination. While our results are promising, it remains to be seen how well it deals with the increased complexity of 3D models over 2D models and larger scale experiments. However, the BMAB model has a large amount of literature to draw from as we encounter new and more challenging problems \cite{bergemann2006bandit}.

@@

\section{Appendix} \label{sec:Appendix}
 In order to solve our problem definition, we must evaluate $P(Q(\Gamma)>0)$ for a given grasp plan $\Gamma$. We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating $P(Q(\Gamma)>0)$ efficiently.

>>>>

\documentclass[journal,transmag]{IEEEtran}% Comment this line out if you need a4paper

@@

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

@@

\usepackage{tikz,hyperref,graphicx,units,subfig}
\usepackage{subfig}
\usepackage{benktools}
\usepackage{caption}
\renewcommand{\captionfont}{\footnotesize}
\usepackage{sidecap,wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\abs}[1]{\lvert#1\rvert} 
\newcommand{\norm}[1]{\lVert#1\rVert}
%\newcommand{\suchthat}{\mid}
\newcommand{\suchthat}{\ \big|\ }
\newcommand{\bd}{\mathbf{d}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bt}{\mathbf{t}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bbf}{\mathbf{f}}
\newcommand{\bzero}{\mathbf{0}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mF}{\mathcal{F}}
\newcommand{\bZ}{\mathbf{Z}}

@@

\begin{abstract}
\textit{Abstract---}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.  This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
\end{abstract}

\begin{abstract}
\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to ucertainities. For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown. To handle all the uncertainites and plan for grasps using a grasp metric, one must perform monte-carlo integration and exhaustively evaluate samples. We show that by using simple algorithms from the Multi-Armed bandit literature, you can intelligently decided which grasp to sample from next and quickly determine the best grasp in a given set of proposed grasps. 
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps . $P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed. Reducing the time to find the grasp with the highest probability of force closure from a set of a large number of grasps is the primary focus of the paper.

Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}. To model this uncertainty we chose to use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Sec. \ref{sec:Appendix}.  A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace. A signed distance function is  greater than 0 outside the surface of an object, 0 at the surface and less than 0 beneath.  The GPIS can be sampled from via $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS. For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape. We will henceforth  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.

@@

@@

 \vspace{-2ex}
 \begin{align*}
 &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
 &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)
 \end{align*}

@@

\subsection{Multi-Armed Bandit Experiments}
We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$. For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. In Fig. \ref{fig:simple_regret}, we plotted the simple regret averaged over 100 of the shapes in our data set and compare the different methods (UCB, Thompson, Gittins and the naive random allocation). We initialize both the Monte-Carlo and bandit technique by sampling each grasp 1 time. We draw samples from our calculated distributions $p(g)$.  Interestingly, Gittins and Thompson converge much faster than random and UCB. In Fig. \ref{fig:pulls_per_grasp}, you can see that Gittins and Thompson allocate grasp samples to only the grasps of high quality, thus it is quickly able to ignore the low quality grasps. UCB takes a more conservative approach to sample allocation, which leads to poor performance in the best arm identification problem \cite{bubeck2009pure}.

@@

\subsection{Sensitivity Analysis }
We now will show how well the one of the top algorithms Thompson Sampling perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose. The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter.

For friction coefficient we started at $\sigma_{\mu} = 0.05$ and enlarged it to $\sigma_{\mu}  = 0.4$. As you can see in Fig. \ref{fig:fric_sens}, the performance of the bandit algorithm remains largely unchanged, with typical convergance in simple regret around 2500 samples or 2.5 samples per grasp for Thompson sampling.

For rotational uncertainity in pose, we varied $\sigma_{rot}$ in the range of $(0.03, 0.24)$ radians. As you can see in Fig. \ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\deg}$  causes the convergence in simple regret to not be reached until 5500 samples or an average of 5.5 samples per grasp. This can be explained because such a large variance causes a a drop in quality across all grasps and makes it harder to separate the outliers \cite{gabillon2012bes}. The quality of the best grasp along with the grasp for each round is shown in \ref{fig:rot_shapes}.

For translational uncertainty in pose, we varied $\sigma_{trans}$ in the range of $(3, 24)$ units (on a 40 x 40 unit workspace). As you can see in Fig. \ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until around 5500 samples or an average of 5.5 samples per grasp.

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_fric.eps}
\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{fric}$ in the range of $(0.05, 0.4)$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set. The increase in noise has little effect on the convergence of Thompson Sampling in simple regret.}
\vspace*{-10pt}
\label{fig:fric_sens}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_rot.eps}
\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{rot}$ in the range of $(0.03, 0.24)$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.  As you can see the increase in noise effects performance, however the 5500 samples needed for convergence at the the highest level of noise (which is over half the workspace) is much less that the samples needed for uniform allocation to converge in Fig. \ref{fig:simple_regret}}
\vspace*{-10pt}
\label{fig:rot_sens}
\end{figure*}

\begin{figure*}%
    \centering
    \subfloat[lTop Grasps Shown for Shape 1]{{\includegraphics[width=16.5cm]{matlab_figures/rot_shapes_1.eps} }}%
    \qquad
    \subfloat[Top Grasps Shown for Shape 2]{{\includegraphics[width=16.5cm]{matlab_figures/rot_shapes_2.eps} }}%
    \caption{Two shapes shown from the Brown Visual Lab Dataset,from Left to Right the variance on rotation $\sigma_{rot}$ is increased from $2^{\deg}$ to $13^{\deg}$. As you can see the overall variance increase effects the quality of the top grasp in the set of possible grasps. Furthermore for Shape 2, the grasp with low rotational variance is different than that for higher variance because the original grasp is more likely to touch the area of higher shape uncertainty when subjected to high variance in rotation.  }%
    \label{fig:rot_shapes}%
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_trans.eps}
\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{trans}$ in the range of $(3,24)$ units from top to bottom on a 40 x 40 unit workspace.  As you can see the increase in noise effects performance, however the 4200 samples needed for convergence at the the highest level of noise (which is over half the workspace) is much less that the samples needed for uniform allocation to converge in Fig. \ref{fig:simple_regret}}
\vspace*{-10pt}
\label{fig:trans_sens}
\end{figure*}

@@

Our budgeted multi-armed bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids. Future work will be building an efficient construction of GPIS to scale to 3D and test the bandit method there.

The methods we showed (UCB, Thompson and Gittins) will always find the best grasp, but when do you terminate the algorithm is still an open question. Fixed confidence methods do exist that terminate when a certain confidence interval is reached \cite{maron1993hoeffding} \cite{mnih2008empirical}. However, a known problem is that if two grasps have very similar quality it could greatly increase the time for need to reach the statistical confidence interval \cite{audibert2010best}. We purpose using the approach of a user setting a fixed budget based  time constraints. How much time the user is willing to allow for grasp evaluation and repeatibility results on a set task can help guide this fixed budget. Our sensitivity analysis showed that even under extreme noise, our MAB approach is still much better than prior approach though, so we expect the fixed budget to be small.

Another problem that was revealed in our analysis was that our current grasp metric, probability of force closure, is not dependent on the center of mass \cite{ferrari1992}. It only measure the probability that a grasp controller can resist any force provided it can exert an infinite force.  One can assume that the grasp controller on a robot hand is powerful enough to apply the proper resistance, but that assumption might be invalid in some non-industrial robotic applications. A similar metric that is still from Beta-Bernoulli and takes center of mass into account, would be ideal for both accurate grasp quality prediction under uncertainty and the utilization of MAB algorithms.  Recent work by Kim et al. developed a physics based simulator that could potentially achieve this goal \cite{kim2012physically}.

\section{Conclusion}
Assessing grasp quality under  uncertainty is computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coeffiecient and motion. 
A key insight from our work is that uniformly allocating samples to grasps is inefficient, and
 we found that a MAB approach prioritizes evaluation of high-quality grasps while quickly pruning-out obviously poor grasps.
A pre-requisite for applying a bandit approach is to formulate a representation  of how uncertainty affects grasp parameters and thus grasp quality.
We purpose treating this as a graphical model and use model the parameters as stochastic noise. Our choice of distributions though is not the focus of the paper and the MAB algorithm will still work independent of this. 
We evaluated this theoretical model on a dataset of common objects and confirmed that: (1) the bandits approach always converged to the best grasp in the candidate set, (2) it converges on average an order of magnitude faster than a uniform sampling approach in our experiments.

@@

Future work will also consider applying BMAB approach to grasp planners like GraspIt! \cite{miller2004graspit} to see if our method can handle uncertainty while working under the time constraints needed for most real time applications. While our results are promising, it remains to be seen how well it deals with the increased complexity of 3D models over 2D models and larger scale experiments. However, the BMAB model has a large amount of literature to draw from as we encounter new and more challenging problems \cite{bergemann2006bandit}.

@@

\appendix[Gaussian Process Implicit Surface for Representing Shape Uncertainty]
 \label{sec:Appendix}
 In order to solve our problem definition, we must evaluate $P(Q(\Gamma)>0)$ for a given grasp plan $\Gamma$. We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating $P(Q(\Gamma)>0)$ efficiently.
